Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-26 paper/structureScene.tex
prior to -> before

Prior to constructing models (for classification or similarity estimation), it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review two transformations which achieve these properties, namely logarithmic compression and standardization.

>>>>

Before constructing models for classification or similarity estimation, it is beneficial to process scattering coefficients to improve invariance, normality, and generalization power.
In this section, we review two transformations which achieve these properties, namely logarithmic compression and standardization.
